---
title: "Reproducible Analysis: Age, Income, and the Discounting of Delayed Monetary Losses"
author: "Haoran Wan, Joel Myerson, Leonard Green, Michael J. Strube, and Sandra Hale"
date: last-modified
params:
  data_file: "Supplementary Data.xlsx"
  fit_models: false
  fit_supplementary: false
  run_power: false
  power_simulations: 5000
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    self-contained: true
    theme: cosmo
execute:
  echo: true
  warning: true
  message: false
engine: knitr
---

## Scope and citation

This document reproduces the analyses reported in:

> Wan, H., Myerson, J., Green, L., Strube, M. J., & Hale, S. (2025). Age, income, and the discounting of delayed monetary losses. *The Journals of Gerontology, Series B: Psychological Sciences and Social Sciences, 80*(11), gbaf162. <https://doi.org/10.1093/geronb/gbaf162>

The study is cross-sectional. Age coefficients describe between-person associations and should not be interpreted as within-person aging effects. Income coefficients are associational and should not be interpreted causally. The study design, hypotheses, and analytic plan were not preregistered, as disclosed in the article.

Participant-level data are not stored in this repository. Download **Supplementary Data** from the [publisher's article page](https://academic.oup.com/psychsocgerontology/article/80/11/gbaf162/8249241#supplementary-data) and save the workbook as `Analysis/Supplementary Data.xlsx`.

Bayesian fitting and the prospective 5,000-replication power analysis are disabled by default because they are computationally intensive. Use the document parameters `fit_models`, `fit_supplementary`, and `run_power` to enable them.

## Reproducibility setup

```{r setup}
set.seed(20250908)
options(mc.cores = min(4L, parallel::detectCores()))

library(bayesplot)
library(brms)
library(cmdstanr)
library(doSNOW)
library(foreach)
library(ggpubr)
library(glmmTMB)
library(Hmisc)
library(minpack.lm)
library(multcomp)
library(posterior)
library(psych)
library(readxl)
library(tidybayes)
library(tidyverse)

theme_set(
  theme_classic(base_size = 11) +
    theme(
      axis.title = element_text(face = "bold"),
      plot.title = element_text(face = "bold"),
      strip.text = element_text(face = "bold"),
      legend.title = element_text(face = "bold")
    )
)

cache_dir <- file.path("cache", "r_models")
output_dir <- "outputs"
dir.create(cache_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
```

### Analysis functions

```{r functions}
two_sd_scale <- function(x) {
  x <- as.numeric(x)
  scale <- 2 * sd(x, na.rm = TRUE)
  if (!is.finite(scale) || scale == 0) {
    stop("Cannot scale a variable with zero or undefined variance.")
  }
  (x - mean(x, na.rm = TRUE)) / scale
}

auc_trapezoid <- function(delay, rsv) {
  ordering <- order(delay)
  x <- delay[ordering] / max(delay[ordering])
  y <- rsv[ordering]
  sum(diff(x) * (y[-1] + y[-length(y)])) / 2
}

move_inside_unit_interval <- function(x) {
  pmin(pmax(x, .Machine$double.xmin), 1 - .Machine$double.eps)
}

probability_direction <- function(x) {
  max(mean(x > 0), mean(x < 0))
}

fit_beta_model <- function(formula, data, file_name) {
  brm(
    formula = formula,
    data = data,
    family = Beta(link = "logit"),
    prior = c(
      # The original code operationalized the article's "flat" priors with
      # extremely diffuse Normal distributions.
      prior(normal(0, 1e200), class = Intercept),
      prior(cauchy(0, 2.5), class = b),
      prior(cauchy(0, 2.5), class = sd),
      prior(normal(0, 1e200), class = phi)
    ),
    chains = 4,
    iter = 4000,
    warmup = 2000,
    cores = min(4L, parallel::detectCores()),
    seed = 20250908,
    backend = "cmdstanr",
    control = list(adapt_delta = 0.95, max_treedepth = 10),
    file = file.path(cache_dir, file_name),
    file_refit = "on_change",
    refresh = 200
  )
}

summarize_fixed_effects <- function(model) {
  posterior::summarise_draws(
    posterior::as_draws_array(model),
    median,
    sd,
    pd = probability_direction,
    posterior::rhat,
    posterior::ess_bulk,
    posterior::ess_tail
  ) |>
    filter(str_starts(variable, "b_")) |>
    mutate(term = str_remove(variable, "^b_")) |>
    select(term, median, sd, pd, rhat, ess_bulk, ess_tail)
}

check_diagnostics <- function(model) {
  diagnostics <- summarize_fixed_effects(model)
  divergences <- sum(nuts_params(model)$Parameter == "divergent__" &
                       nuts_params(model)$Value == 1)
  tibble(
    divergences = divergences,
    maximum_rhat = max(diagnostics$rhat, na.rm = TRUE),
    minimum_bulk_ess = min(diagnostics$ess_bulk, na.rm = TRUE),
    minimum_tail_ess = min(diagnostics$ess_tail, na.rm = TRUE)
  )
}
```

## Data import and validation

The supplementary workbook stores monetary amount in dollars; it is therefore log-transformed directly. Treating `Amount` as the historical category codes 1-3 would be incorrect for this public workbook.

```{r data-import}
if (!file.exists(params$data_file)) {
  stop(
    "Missing ", params$data_file,
    ". Download Supplementary Data from the publisher and place it in Analysis/."
  )
}

required_columns <- c(
  "ID", "Age", "Income", "Education", "Gender", "Anxiety", "Depression",
  "Distress", "Health", "Ethnicity", "Race", "Amount", "Delay", "RSV"
)

raw <- read_excel(params$data_file, sheet = "Data")
missing_columns <- setdiff(required_columns, names(raw))
if (length(missing_columns) > 0) {
  stop("Missing required columns: ", paste(missing_columns, collapse = ", "))
}

validation <- list(
  participants = n_distinct(raw$ID) == 594,
  rows = nrow(raw) == 8910,
  amounts = identical(sort(unique(raw$Amount)), c(150, 2500, 30000)),
  delays = identical(sort(unique(raw$Delay)), c(1, 3, 12, 36, 120)),
  observations_per_participant = all(count(raw, ID)$n == 15),
  age_range = all(between(raw$Age, 20, 80))
)
if (!all(unlist(validation))) {
  stop("Supplementary-data validation failed: ",
       paste(names(validation)[!unlist(validation)], collapse = ", "))
}

raw <- raw |>
  mutate(
    across(c(Age, Income, Education, Gender, Anxiety, Depression, Distress,
             Health, Ethnicity, Race, Amount, Delay, RSV), as.numeric),
    Age_group = factor(
      case_when(
        Age >= 20 & Age < 35 ~ "20-34",
        Age >= 35 & Age <= 50 ~ "35-50",
        Age > 50 & Age < 65 ~ "51-64",
        Age >= 65 & Age <= 80 ~ "65-80"
      ),
      levels = c("20-34", "35-50", "51-64", "65-80")
    ),
    Amount_log = log(Amount)
  )

tibble(
  participants = n_distinct(raw$ID),
  task_rows = nrow(raw),
  minimum_age = min(raw$Age),
  maximum_age = max(raw$Age)
)
```

## Outcome construction and analysis samples

AuC is calculated separately for each participant and amount after dividing each delay by the maximum delay. Larger AuC values indicate shallower discounting of the delayed loss. Values at the boundaries are moved to the nearest representable value inside `(0, 1)` because the beta likelihood excludes exact zeros and ones.

```{r data-preparation}
demographics <- raw |>
  distinct(ID, Age, Age_group, Income, Education, Gender, Anxiety, Depression,
           Distress, Health, Ethnicity, Race)

auc_data <- raw |>
  group_by(ID, Amount_log) |>
  summarise(AuC = auc_trapezoid(Delay, RSV), .groups = "drop") |>
  left_join(demographics, by = "ID", relationship = "many-to-one") |>
  mutate(AuC = move_inside_unit_interval(AuC)) |>
  arrange(ID, Amount_log)

model_1_data <- auc_data |>
  filter(Age >= 35) |>
  mutate(Age_std = two_sd_scale(Age))

model_2_data <- auc_data |>
  filter(Age >= 35, !is.na(Income)) |>
  mutate(
    Age_std = two_sd_scale(Age),
    Income_std = two_sd_scale(Income)
  )

model_3_data <- auc_data |>
  filter(Age >= 35, if_all(c(Income, Anxiety, Depression, Distress), ~ !is.na(.x))) |>
  mutate(
    Age_std = two_sd_scale(Age),
    Income_std = two_sd_scale(Income),
    Anxiety_std = two_sd_scale(Anxiety),
    Depression_std = two_sd_scale(Depression),
    Distress_std = two_sd_scale(Distress)
  )

model_4_data <- auc_data |>
  filter(
    Age >= 35,
    if_all(c(Income, Education, Gender, Anxiety, Depression, Distress, Health),
           ~ !is.na(.x))
  ) |>
  mutate(
    Age_std = two_sd_scale(Age),
    Amount_std = two_sd_scale(Amount_log),
    Income_std = two_sd_scale(Income),
    Education_std = two_sd_scale(Education),
    Gender_c = Gender - mean(Gender),
    Anxiety_std = two_sd_scale(Anxiety),
    Depression_std = two_sd_scale(Depression),
    Distress_std = two_sd_scale(Distress),
    Health_std = two_sd_scale(Health)
  )

tibble(
  model = c("Model 1", "Model 2", "Model 3", "Model 4"),
  participants = c(
    n_distinct(model_1_data$ID),
    n_distinct(model_2_data$ID),
    n_distinct(model_3_data$ID),
    n_distinct(model_4_data$ID)
  ),
  observations = c(nrow(model_1_data), nrow(model_2_data),
                   nrow(model_3_data), nrow(model_4_data))
)
```

## Descriptive analyses

### Group-level discounting functions (Figure 1)

```{r figure-1, fig.width=10.5, fig.height=3.2}
group_discounting <- raw |>
  mutate(
    Amount_label = factor(
      scales::dollar(Amount, accuracy = 1),
      levels = c("$150", "$2,500", "$30,000")
    )
  ) |>
  group_by(Age_group, Amount_label, Delay) |>
  summarise(Mean_RSV = mean(RSV), .groups = "drop")

figure_1 <- group_discounting |>
  arrange(desc(Amount_label)) |>
  ggplot(aes(Delay, Mean_RSV, color = Amount_label, shape = Amount_label,
             linetype = Amount_label)) +
  geom_smooth(
    method = "nlsLM",
    formula = y ~ 1 / (1 + exp(log_k) * x)^s,
    method.args = list(start = list(log_k = -4, s = 0.5)),
    se = FALSE,
    linewidth = 0.7,
    show.legend = FALSE
  ) +
  geom_point(size = 2.4, fill = "white") +
  facet_wrap(~ Age_group, nrow = 1) +
  scale_color_manual(values = c("#33a02c", "#ff7f00", "#1f78b4")) +
  scale_shape_manual(values = c(22, 24, 21)) +
  scale_linetype_manual(values = c("dotted", "dashed", "solid")) +
  scale_x_continuous(breaks = c(1, 36, 120)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Delay (months)", y = "Relative subjective value",
       color = "Amount", shape = "Amount", linetype = "Amount")

figure_1
ggsave(file.path(output_dir, "figure_1_r.png"), figure_1,
       width = 10.5, height = 3.2, dpi = 300)
```

The article reported that the hyperboloid function accounted for more than 87% of the variance in every age-group-by-amount series.

```{r hyperboloid-fit}
hyperboloid_fit <- group_discounting |>
  group_by(Age_group, Amount_label) |>
  group_modify(
    ~ {
      model <- nlsLM(
        Mean_RSV ~ 1 / (1 + k * Delay)^s,
        data = .x,
        start = list(k = 0.1, s = 1),
        lower = c(k = 0, s = 0)
      )
      fitted_values <- fitted(model)
      tibble(
        R2 = 1 - sum((.x$Mean_RSV - fitted_values)^2) /
          sum((.x$Mean_RSV - mean(.x$Mean_RSV))^2)
      )
    }
  )

hyperboloid_fit
```

### Amount contrasts and reliability

The published amount analysis compared the largest loss with the smallest loss and then the largest with the middle loss within each age group using beta mixed models with participant random intercepts.

```{r amount-contrasts}
amount_contrasts <- auc_data |>
  group_by(Age_group) |>
  group_modify(
    ~ {
      model <- glmmTMB(
        AuC ~ -1 + factor(Amount_log) + (1 | ID),
        family = beta_family(link = "logit"),
        data = .x
      )
      tibble(
        contrast = c("$30,000 - $150", "$30,000 - $2,500"),
        p_value = c(
          summary(glht(model, linfct = matrix(c(-1, 0, 1), nrow = 1)))$test$pvalues,
          summary(glht(model, linfct = matrix(c(0, -1, 1), nrow = 1)))$test$pvalues
        )
      )
    }
  )

amount_contrasts

reliability_data <- auc_data |>
  select(ID, Amount_log, AuC) |>
  pivot_wider(names_from = Amount_log, values_from = AuC)

psych::alpha(select(reliability_data, -ID), check.keys = FALSE)$total
```

### Correlations and age-group means

```{r correlations}
participant_data <- auc_data |>
  group_by(ID) |>
  summarise(
    across(c(Age, Income, Education, Gender, Distress, Anxiety, Depression,
             Health, AuC), ~ mean(.x, na.rm = TRUE)),
    Age_group = first(Age_group),
    .groups = "drop"
  )

correlation_20_80 <- participant_data |>
  select(Age, Income, Education, Gender, Distress, Anxiety, Depression, Health, AuC) |>
  as.matrix() |>
  rcorr(type = "pearson")

correlation_35_80 <- participant_data |>
  filter(Age >= 35) |>
  select(Age, Income, Education, Gender, Distress, Anxiety, Depression, Health, AuC) |>
  as.matrix() |>
  rcorr(type = "pearson")

round(correlation_20_80$r, 3)
round(correlation_35_80$r, 3)

tibble(
  test = c("Age and mean AuC, ages 20-80",
           "Income and mean AuC, ages 20-34",
           "Income and mean AuC, ages 35-80"),
  r = c(
    cor(participant_data$Age, participant_data$AuC, use = "complete.obs"),
    with(filter(participant_data, Age < 35),
         cor(Income, AuC, use = "complete.obs")),
    with(filter(participant_data, Age >= 35),
         cor(Income, AuC, use = "complete.obs"))
  )
)
```

```{r figure-2, fig.width=4.2, fig.height=3.6}
age_group_summary <- participant_data |>
  group_by(Age_group) |>
  summarise(
    mean_AuC = mean(AuC),
    standard_error = sd(AuC) / sqrt(n()),
    .groups = "drop"
  )

figure_2 <- ggplot(age_group_summary, aes(Age_group, mean_AuC, fill = Age_group)) +
  geom_col(color = "black", width = 0.75, show.legend = FALSE) +
  geom_errorbar(
    aes(ymin = mean_AuC - standard_error, ymax = mean_AuC + standard_error),
    width = 0.18
  ) +
  scale_fill_manual(values = c("#C6DBEF", "#73A1CC", "#3A6EAA", "#08306B")) +
  coord_cartesian(ylim = c(0.2, 1.0)) +
  labs(x = "Age group", y = "Area under the curve")

figure_2
ggsave(file.path(output_dir, "figure_2_r.png"), figure_2,
       width = 4.2, height = 3.6, dpi = 300)
```

## Prospective power analysis

The article's prospective simulation used a random-intercept beta regression, `phi = 12.2`, participant-intercept SD `0.944`, coefficients `log(1.5)` after two-SD scaling, approximately 100 participants per age decade, and 5,000 simulated data sets. This section is deliberately opt-in.

```{r power-analysis, eval=params$run_power}
simulate_power <- function(n_per_decade = 100, beta_age = log(1.5),
                           beta_income = log(1.5), phi = 12.2,
                           participant_sd = 0.944, simulations = 5000) {
  cluster <- parallel::makeCluster(min(4L, parallel::detectCores()))
  on.exit(parallel::stopCluster(cluster), add = TRUE)
  registerDoSNOW(cluster)

  results <- foreach(
    simulation = seq_len(simulations),
    .combine = rbind,
    .packages = c("glmmTMB", "dplyr")
  ) %dopar% {
    participant <- seq_len(n_per_decade * 6)
    age <- c(
      runif(n_per_decade, 20, 29), runif(n_per_decade, 30, 39),
      runif(n_per_decade, 40, 49), runif(n_per_decade, 50, 59),
      runif(n_per_decade, 60, 69), runif(n_per_decade, 70, 80)
    )
    income <- rbinom(length(participant), 4, 0.5) + 1
    random_intercept <- rnorm(length(participant), 0, participant_sd)

    simulated <- tibble(
      ID = factor(rep(participant, each = 3)),
      Age = rep(age, each = 3),
      Income = rep(income, each = 3),
      random_intercept = rep(random_intercept, each = 3)
    ) |>
      mutate(
        Age_std = two_sd_scale(Age),
        Income_std = two_sd_scale(Income),
        mu = plogis(random_intercept + beta_age * Age_std + beta_income * Income_std),
        AuC = rbeta(n(), mu * phi, (1 - mu) * phi),
        AuC = move_inside_unit_interval(AuC)
      )

    restricted <- simulated |>
      filter(Age >= 35) |>
      mutate(
        Age_std = two_sd_scale(Age),
        Income_std = two_sd_scale(Income)
      )

    tryCatch({
      full_fit <- glmmTMB(AuC ~ Age_std + (1 | ID),
                          family = beta_family(), data = simulated)
      restricted_fit <- glmmTMB(AuC ~ Age_std + Income_std + (1 | ID),
                                family = beta_family(), data = restricted)
      c(
        age_20_80 = coef(summary(full_fit))$cond["Age_std", "Pr(>|z|)"],
        age_35_80 = coef(summary(restricted_fit))$cond["Age_std", "Pr(>|z|)"],
        income_35_80 = coef(summary(restricted_fit))$cond["Income_std", "Pr(>|z|)"]
      )
    }, error = function(error) c(NA_real_, NA_real_, NA_real_))
  }

  colMeans(results < 0.05, na.rm = TRUE)
}

power_cache <- file.path(cache_dir, "prospective_power.rds")
if (file.exists(power_cache)) {
  power_estimates <- readRDS(power_cache)
} else {
  power_estimates <- simulate_power(simulations = params$power_simulations)
  saveRDS(power_estimates, power_cache)
}

enframe(power_estimates, name = "coefficient", value = "estimated_power")
```

## Bayesian multilevel beta regressions

The article used four chains of 4,000 iterations, discarded the first 2,000 iterations of each chain, and summarized posterior medians, posterior SDs, and probability of direction (`pd`). It treated `pd > .975` as statistically significant. The original R code operationalized the article's flat priors for the intercept and precision as extremely diffuse `Normal(0, 1e200)` priors. The main fixed-effect model sequence is:

1. age and age²;
2. Model 1 plus income;
3. Model 2 plus anxiety; and
4. all pairwise interactions among age, income, anxiety, log amount, education, gender, and health, plus age².

Models 1-3 use participant random intercepts. Model 4 uses a correlated participant random intercept and log-amount slope. Table 3 in the article displays the Model 4 main effects and age interactions; the complete pairwise-interaction output appears in Supplementary Table 2.

```{r main-models, eval=params$fit_models}
model_1 <- fit_beta_model(
  AuC ~ Age_std + I(Age_std^2) + (1 | ID),
  model_1_data,
  "model_1"
)

model_2 <- fit_beta_model(
  AuC ~ Age_std + I(Age_std^2) + Income_std + (1 | ID),
  model_2_data,
  "model_2"
)

model_3 <- fit_beta_model(
  AuC ~ Age_std + I(Age_std^2) + Income_std + Anxiety_std + (1 | ID),
  model_3_data,
  "model_3"
)

model_4 <- fit_beta_model(
  AuC ~
    (Age_std + Income_std + Anxiety_std + Amount_std + Education_std +
       Gender_c + Health_std)^2 +
    I(Age_std^2) +
    (1 + Amount_std | ID),
  model_4_data,
  "model_4"
)

model_summaries <- list(
  Model_1 = summarize_fixed_effects(model_1),
  Model_2 = summarize_fixed_effects(model_2),
  Model_3 = summarize_fixed_effects(model_3),
  Model_4 = summarize_fixed_effects(model_4)
)

model_summaries
bind_rows(lapply(list(model_1, model_2, model_3, model_4), check_diagnostics),
          .id = "model")
```

### Published Model 4 contrasts

```{r model-4-contrasts, eval=params$fit_models}
model_4_draws <- posterior::as_draws_df(model_4)

income_values <- sort(unique(model_4_data$Income_std))
amount_values <- sort(unique(model_4_data$Amount_std))

contrast_draws <- model_4_draws |>
  transmute(
    age_at_low_income = 0.5 *
      (`b_Age_std` + `b_Age_std:Income_std` * income_values[1]) +
      0.5 * (`b_Age_std` + `b_Age_std:Income_std` * income_values[2]),
    age_at_middle_income =
      `b_Age_std` + `b_Age_std:Income_std` * income_values[3],
    age_at_high_income = 0.5 *
      (`b_Age_std` + `b_Age_std:Income_std` * income_values[4]) +
      0.5 * (`b_Age_std` + `b_Age_std:Income_std` * income_values[5]),
    age_at_150 = `b_Age_std` + `b_Age_std:Amount_std` * amount_values[1],
    age_at_2500 = `b_Age_std` + `b_Age_std:Amount_std` * amount_values[2],
    age_at_30000 = `b_Age_std` + `b_Age_std:Amount_std` * amount_values[3]
  ) |>
  pivot_longer(everything(), names_to = "contrast", values_to = "draw") |>
  group_by(contrast) |>
  summarise(
    median = median(draw),
    posterior_sd = sd(draw),
    pd = probability_direction(draw),
    .groups = "drop"
  )

contrast_draws
```

### Figures 3 and 4

```{r figures-3-4, eval=params$fit_models, fig.width=9, fig.height=3.8}
age_grid <- tibble(Age = seq(35, 80, by = 1)) |>
  mutate(Age_std = (Age - mean(model_1_data$Age)) / (2 * sd(model_1_data$Age)))

figure_3_data <- age_grid |>
  add_epred_draws(model_1, re_formula = NA) |>
  group_by(Age) |>
  median_qi(.epred, .width = 0.95)

figure_3 <- ggplot(figure_3_data, aes(Age, .epred)) +
  geom_ribbon(aes(ymin = .lower, ymax = .upper), fill = "#b2182b", alpha = 0.18) +
  geom_line(color = "#b2182b", linewidth = 1) +
  coord_cartesian(ylim = c(0.2, 1.0)) +
  labs(x = "Age", y = "Area under the curve")

income_grid <- expand_grid(Age = seq(35, 80), Income = 1:5) |>
  mutate(
    Age_std = (Age - mean(model_4_data$Age)) / (2 * sd(model_4_data$Age)),
    Income_std = (Income - mean(model_4_data$Income)) / (2 * sd(model_4_data$Income)),
    Amount_std = 0,
    Education_std = 0,
    Gender_c = 0,
    Anxiety_std = 0,
    Health_std = 0,
    Income_group = factor(
      case_when(Income <= 2 ~ "<$50K", Income == 3 ~ "$50-80K", TRUE ~ ">$80K"),
      levels = c(">$80K", "$50-80K", "<$50K")
    )
  ) |>
  add_epred_draws(model_4, re_formula = NA) |>
  group_by(Age, Income_group, .draw) |>
  summarise(.epred = mean(.epred), .groups = "drop") |>
  group_by(Age, Income_group) |>
  summarise(.epred = median(.epred), .groups = "drop")

amount_grid <- expand_grid(Age = seq(35, 80), Amount = c(150, 2500, 30000)) |>
  mutate(
    Age_std = (Age - mean(model_4_data$Age)) / (2 * sd(model_4_data$Age)),
    Amount_std = (log(Amount) - mean(model_4_data$Amount_log)) /
      (2 * sd(model_4_data$Amount_log)),
    Income_std = 0,
    Education_std = 0,
    Gender_c = 0,
    Anxiety_std = 0,
    Health_std = 0,
    Amount_label = factor(scales::dollar(Amount, accuracy = 1),
                          levels = c("$150", "$2,500", "$30,000"))
  ) |>
  add_epred_draws(model_4, re_formula = NA) |>
  group_by(Age, Amount_label) |>
  summarise(.epred = median(.epred), .groups = "drop")

income_panel <- ggplot(income_grid, aes(Age, .epred, color = Income_group,
                                        linetype = Income_group)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("#b15928", "#6a3d9a", "#e31a1c")) +
  scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
  coord_cartesian(ylim = c(0.2, 1.0)) +
  labs(x = "Age", y = "Area under the curve", color = "Income", linetype = "Income")

amount_panel <- ggplot(amount_grid, aes(Age, .epred, color = Amount_label,
                                        linetype = Amount_label)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("#33a02c", "#ff7f00", "#1f78b4")) +
  scale_linetype_manual(values = c("dotted", "dashed", "solid")) +
  coord_cartesian(ylim = c(0.2, 1.0)) +
  labs(x = "Age", y = "Area under the curve", color = "Amount", linetype = "Amount")

figure_3
figure_4 <- ggarrange(income_panel, amount_panel, ncol = 2)
figure_4

ggsave(file.path(output_dir, "figure_3_r.png"), figure_3,
       width = 4.2, height = 3.6, dpi = 300)
ggsave(file.path(output_dir, "figure_4_r.png"), figure_4,
       width = 9, height = 3.8, dpi = 300)
```

## Supplementary depression and distress models

These models replace anxiety with depression or total HADS distress. They are separated from the primary model sequence and are opt-in.

```{r supplementary-models, eval=params$fit_supplementary}
depression_model <- fit_beta_model(
  AuC ~ Age_std + I(Age_std^2) + Income_std + Depression_std + (1 | ID),
  model_3_data,
  "supplementary_depression"
)

depression_full_model <- fit_beta_model(
  AuC ~
    (Age_std + Income_std + Depression_std + Amount_std + Education_std +
       Gender_c + Health_std)^2 +
    I(Age_std^2) +
    (1 + Amount_std | ID),
  model_4_data,
  "supplementary_depression_full"
)

distress_model <- fit_beta_model(
  AuC ~ Age_std + I(Age_std^2) + Income_std + Distress_std + (1 | ID),
  model_3_data,
  "supplementary_distress"
)

distress_full_model <- fit_beta_model(
  AuC ~
    (Age_std + Income_std + Distress_std + Amount_std + Education_std +
       Gender_c + Health_std)^2 +
    I(Age_std^2) +
    (1 + Amount_std | ID),
  model_4_data,
  "supplementary_distress_full"
)

list(
  depression = summarize_fixed_effects(depression_model),
  depression_full = summarize_fixed_effects(depression_full_model),
  distress = summarize_fixed_effects(distress_model),
  distress_full = summarize_fixed_effects(distress_full_model)
)
```

## Session information

```{r session-information}
sessionInfo()
cmdstanr::cmdstan_version()
```
